{{ cookiecutter.paper_title}}

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Added spaces
Trying new syntax

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \mailto{{{ cookiecutter.author_email }}}}\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}

>>>>

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \href{mailto:{{ cookiecutter.author_email }}}{ {{ cookiecutter.author_email }} } }\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}
